The Small World Network Effect in Software Project Teams \author{Kevin Peterson\\ \small \texttt{pete1968@umn.edu} }

### 2013-11-26 paper/main.tex
Added SourceForge data.
Updated var names.

\noindent\\\textit{\textbf{Clustering Coefficient - Transitivity ($C$)}}\\
We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[C^\Delta = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

@@

\noindent\\\textit{\textbf{Clustering Coefficient - Average ($\overline{C}$)}}\\
Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.

@@

Given this \textit{neighborhood}, we can then calculate how closely connected the nodes are. To do this, we take the number of actual connections between neighbors divided by the total possible number of connections, where $k_i$ represents the count of the neighbors of a node, or {$k_i = |N_i|$}
\[ C_i = \frac{2|\{e_{jk}: v_j,v_k \in N_i, e_{jk} \in E\}|}{k_i(k_i-1)} \]

From this \textit{Local Clustering Coefficient} $\overline{C_i}$, we can then take the average over the entire set of nodes in the graph.
\[ \overline{C^\Delta} = \frac{1}{|P|}\sum^{|P|}_{i=1}C_i \]

It is important to note that although the terminology is similar\cite{uzzi2005collaboration}, $\overline{C^\Delta}$ and $C^\Delta$ are different measurements. Unless otherwise noted, the Transitivity version of this metric ($C^\Delta$) will be used for all further calculations and metrics.

@@

We assume for throughout that any graph exhibiting $Qa > 1$ is a small-world graph.

@@

\input{tables/subgraphs_summary}

@@

$C$ and $\overline{C}$ both indicate values approaching 1. This observation indicates a high degree of clustering\cite{watts1998collective}. hat any indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of close to either 0 or 1. Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
\end{center}
\caption{$Q$ and Project Popularity}
\label{fig:cc_graph}
\end{figure}

Distribution of $Q$ values are shown in figure\ref{fig:q_distribution}. The values of $Q$ generally follow a power-law distribution, with most values being at our around $Q = 1$. This indicates that many graphs are close to the delineation of being considered small-world\cite{humphries2008network}.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-q-histo.png}
\end{center}
\caption{$Q$ Distribution}
\label{fig:q_distribution}
\end{figure}

>>>>

\noindent\\\textit{\textbf{Clustering Coefficient - Transitivity ($C^\Delta$)}}\\
We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[C^\Delta = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

@@

\noindent\\\textit{\textbf{Clustering Coefficient - Average ($\overline{C^{\lambda}}$)}}\\
Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.

@@

Given this \textit{neighborhood}, we can then calculate how closely connected the nodes are. To do this, we take the number of actual connections between neighbors divided by the total possible number of connections, where $k_i$ represents the count of the neighbors of a node, or {$k_i = |N_i|$}
\[ C^{\lambda}_i = \frac{2|\{e_{jk}: v_j,v_k \in N_i, e_{jk} \in E\}|}{k_i(k_i-1)} \]

From this \textit{Local Clustering Coefficient} $C_i$, we can then take the average over the entire set of nodes in the graph.
\[ \overline{C^\lambda} = \frac{1}{|P|}\sum^{|P|}_{i=1}C^{\lambda}_i \]

It is important to note that although the terminology is similar\cite{uzzi2005collaboration}, $\overline{C^\lambda}$ and $C^\Delta$ are different measurements. Unless otherwise noted, the Transitivity version of this metric ($C^\Delta$) will be used for all further calculations and metrics.

@@

We assume for throughout that any graph exhibiting {$Q > 1$} is a small-world graph.

@@

\input{tables/subgraphs_summary_freecode}
\input{tables/subgraphs_summary_sf}

@@

$C^\Delta$ and $\overline{C^\lambda}$ both indicate values approaching 1. This observation indicates a high degree of clustering\cite{watts1998collective}. hat any indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of close to either 0 or 1. Exploring this phenomenon further, we can derive that most graphs resemble the middle or the bottom graph in figure \ref{fig:example_graphs}, with relatively few resembling the top graph.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
\end{center}
\caption{$Q$ and Project Popularity}
\label{fig:q_fc_graph}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{images/sf-graph.png}
\end{center}
\caption{$Q$ and Project Popularity}
\label{fig:q_sf_graph}
\end{figure}

Distribution of $Q$ values are shown in figures\ref{fig:fc_q_distribution,fig:sf_q_distribution}. The values of $Q$ generally follow a power-law distribution, with most values being at our around {$Q = 1$}. This indicates that many graphs are close to the delineation of being considered small-world\cite{humphries2008network}.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-q-histo.png}
\end{center}
\caption{$Q$ Distribution}
\label{fig:q_fc_distribution}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{images/sf-q-histo.png}
\end{center}
\caption{$Q$ Distribution}
\label{fig:q_sf_distribution}
\end{figure}
